`phyr`: An R package for model-based phylogenetic analyses in community ecology

### 2019-06-26 ms.Rmd
update [skip ci]

Two functions (`cor_phylo` and `binaryPGLMM`) were included in this group. Both of them were included in the R package `ape` [@ape2018] orginally.

@@

```{r eval=T}
microbenchmark::microbenchmark(phyr::pcd(comm = comm_a, tree = phylotree, reps = 1000, verbose = F),
                               picante::pcd(comm = comm_a, tree = phylotree, reps = 1000),
                               times = 30)
rt = ape::rtree(n = 1000)
microbenchmark::microbenchmark(phyr::vcv2(rt, corr = T),
                               ape::vcv(rt, corr = T))

>>>>

Two functions (`cor_phylo` and `binaryPGLMM`) were included in this group. Both of them were included in the R package `ape` [@ape2018] originally.

@@

```{r eval=F}
microbenchmark::microbenchmark(phyr::pcd(comm = comm_a, tree = phylotree, reps = 1000, verbose = F),
                               picante::pcd(comm = comm_a, tree = phylotree, reps = 1000),
                               times = 30)
rt = ape::rtree(n = 1000)
microbenchmark::microbenchmark(phyr::vcv2(rt, corr = T),
                               ape::vcv(rt, corr = T))
